A Type System for Safe and Scalable Parallelism using Logical Regions \\ (Extended Version)

### 2012-07-16 doc/popl2013full/langdef.tex
proof

\item Case [E-Read].
By assumption, $\opsenv{\text{read}(e)}{v}{E \dplus [ read(l,excl,v) ]}$ and
$\typeenv{\text{read}(e)}{T}$ and
$\mapconsist{\Omega}$ and 
$\localconsist{L}{\Gamma}$ and 
$\storeconsist{S}{H}$.

>>>>

\item Case [E-Read].
By assumption, $$\opsenv{\text{read}(e)}{v}{E \dplus [ read(l,excl,v) ]}$$ and
$$\typeenv{\text{read}(e)}{T}$$ and
$\mapconsist{\Omega}$ and 
$\localconsist{L}{\Gamma}$ and 
$\storeconsist{S}{H}$.
